### 2014-11-01 BME 560/proposal.tex
New folder for BME 560; gitignored.

\documentclass{article}
\usepackage{tgbonum}
\usepackage{graphicx}
\title{Research Paper: Proposal}
\author{Rahul Krishna \\ 200020531}
\date{\today}
\begin{document}
	\maketitle
	\section{Introduction}
	\begin{list}{--}
	\item In the reseach paper for this term I plan on exploring Intensity Modulated Radiotherapy. 
	\item At the time the refered survey paper was complied, the technique was relatively new and implemented in only a few imaging centers around the world. In my survey, I'll include the results of some comparative studies and clinical trials that have been performed to show the efficacy of IMRT.
	\item The two types of tomotherapy-- linear and helical tomotheraphy. 
	\item Dose distribution
	\item Challenges in tomotherapy 
	\end{list}\end{document}

### 2014-11-01 BME 560/proposal.tex
Final

@@
-\documentclass{article}
+\documentclass[12pt]{article}
 \usepackage{tgbonum}
 \usepackage{graphicx}
+%\usepackage{natbib}
+\linespread{1}
+\setlength{\parindent}{0em}
+\setlength{\parskip}{0.735em}
+\usepackage{fullpage}
 \title{Research Paper: Proposal}
 \author{Rahul Krishna \\ 200020531}
+\usepackage{cite}
+%\usepackage{hyperref}
 \date{\today}
@@
 \maketitle
-	\section{Introduction}
-	\begin{list}{--}
-	\item In the reseach paper for this term I plan on exploring Intensity Modulated Radiotherapy. 
-	\item At the time the refered survey paper was complied, the technique was relatively new and implemented in only a few imaging centers around the world.
-In my survey, I'll include the results of some comparative studies and clinical trials that have been performed to show the efficacy of IMRT.
-	\item The two types of tomotherapy-- linear and helical tomotheraphy. 
-	\item Dose distribution
-	\item Challenges in tomotherapy 
-	\end{list}\end{document}
+\section* {Introduction}
+My survey paper for this will be based on two comprehensive papers on intensity modulated tomotherapy Refs.
+\cite{IMRT2001}, \cite{Mackie2006}.
+In the paper, I will provide a comprehensive description of the following --- the history and early development that led to this form of radiotherapy, Serial and Helical Tomotherapy, the recent advances in the field, and the clinical implementation.
+
+In addition, I will present a comparision between the two types of tomotherapy namely, Serial Tomotherapy and Helical Tomotherapy.
+It is my understanding that the technique is still relatively new and at the time Ref.
+\cite{IMRT2001} was complied, the technique was implemented in only a few imaging centers around the world.
+And therefore, in my survey, I will include the results of some comparative studies and clinical trials that have been performed since to show the efficacy of tomotherapy, both serial and helical.
+
+Moreover, the results of dose distribution will be provided and I will  contrast it with other radiotherapy methods.
+I will also dedicate a section in the paper to discuss the challenges in tomotherapy and what is being done to overcome it.
+\bibliography{proposal}{}
+\bibliographystyle{ieeetr}
+\end{document}

### 2014-11-30 BME 560/Paper.tex
Final Paper

\documentclass[12pt,journal,compsoc]{IEEEtran}
\usepackage{graphicx}
\graphicspath{ {./_figures/} }
\setlength\fboxsep{1pt}
\setlength\fboxrule{1pt}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{times}

\begin{document}
  \markboth{BME 560 Medical Imaging: X-ray, CT, and Nuclear Methods. Fall, 2014}%
  {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}

  \title{Intensity Modulated Radiation Therapy using Tomotherapy}
  \author{Rahul Krishna, 
  \IEEEauthorblockA{\normalsize {\textit{Dept. of Electrical and Computer Engineering}\\
    North Carolina State University, Email: \href{mailto:rkrish11@ncsu.edu}{{rkrish11@ncsu.edu}}}}}

	\IEEEcompsoctitleabstractindextext{%
  \begin{abstract}
    Tomotherapy is a form of 3D-conformal radiotherapy which involves the delivery of intensity modulated radiation therapy (IMRT) using rotational fan beam in a manner quite similar to that seen in modern CT scanners. The modern tomotherapy systems have a couch and gantry which are in continuous motion, closely resembeling the traditional helical-CT systems. This kind of radiotherapy is hence called helical tomotherapy. Helical tomotherapy delivers IMRT based on the images of the patient in the treatment position, and these systems do this by acquiring CT images of the patient. This paper is a discourse on the current state-of-the-art in the field, foucsing primarily the technique's conceptual working and results of its clinical implementation. 
  \end{abstract}
  % IEEEtran.cls defaults to using nonbold math in the Abstract.
  % This preserves the distinction between vectors and scalars. However,
  % if the journal you are submitting to favors bold math in the abstract,
  % then you can use LaTeX's standard command \boldmath at the very start
  % of the abstract to achieve this. Many IEEE journals frown on math
  % in the abstract anyway. In particular, the Computer Society does
  % not want either math or citations to appear in the abstract.

  % Note that keywords are not normally used for peerreview papers.
  \begin{IEEEkeywords}
    Tomotherapy, Intensity Modulated Radiation Therapy.
  \end{IEEEkeywords}}
  \maketitle

  \section{Introduction}
	\IEEEPARstart{T}{he} past couple of decades have seen tremendous advances in radiation oncology. The advent of faster and smaller computers has helped transform the field of radiation therapy and treatment planning. The term tomotherapy translates to ``slice therapy'', and it is derived from tomography.

  \begin{figure*}[t!]
	\includegraphics[width=\linewidth]{tomoblockdiagram}
  \caption{A traditional tomotherapy unit, Ref \cite{Mackie1993}. (a) A block diagram showing the ring gantry in a traditional tomotherapy unit.  }
  \end{figure*}

\end{document}

### 2014-11-30 BME 560/Paper.tex
Updates

@@
-\documentclass[12pt,journal,compsoc]{IEEEtran}
+\documentclass[12pt,journal,compsoc]{IEEEtran} %draftclsnofoot, 
 \usepackage{graphicx}
@@
 \usepackage{amsmath}
+\setlength{\parindent}{0em}
+\setlength{\parskip}{1em}
 \usepackage{hyperref}
+\hypersetup{
+  colorlinks = false,
+  hidelinks = true
+	}
 \usepackage[english]{babel}
@@
 \usepackage{times}
+\usepackage{cite}
 
@@
   \markboth{BME 560 Medical Imaging: X-ray, CT, and Nuclear Methods. Fall, 2014}%
-  {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
+  {BME 560 Medical Imaging: X-ray, CT, and Nuclear Methods. Fall, 2014}
 
@@
 This paper is a discourse on the current state-of-the-art in the field, foucsing primarily the technique's conceptual working and results of its clinical implementation.
+
   \end{abstract}
@@
 The term tomotherapy translates to ``slice therapy'', and it is derived from tomography.
+The system is designed to make use of the tomographic reconstruction mathematics for treatment and also for verification.
+The idea was conceived to tackle several major issues that plagued radiation oncology.
+One of the primary issues was the limitation of target dose that can be delivered due to the presence of neighboring sensitive sturctures.
+One of the potential solutions to avoiding this was to make use of multiple radiation beams with non-uniform beam intensities.
+This method allows us to conform the radiation to the target region thereby sparing the sensitive normal structures which would otherwise prevent normal dose delivery to the affected region.
 
+  The setup has a linear accelerator mounted on a rotating gantry as seen in CT sacnners.
+The radiation is delivered to a patient in a helical way, obtained by concurrent gantry rotation and couch/patient travel as shown in Fig.
+\ref{fig1}.
+In general, the helical tomotherapy units have significantly different radiation fields when compared to other radiotherapy systems.
+This difference can be owed to the absence of absence of a flattening filter, a thin target, an electron stopper, a beam hardener and a compact primary collimator.
+And for this reason, this paper will briefly highlight the radiation characteristics of the helical tomotherapy unit, especially in parts where it differs from standard accelerators.
   \begin{figure*}[t!]
-	\includegraphics[width=\linewidth]{tomoblockdiagram}
-  \caption{A traditional tomotherapy unit, Ref \cite{Mackie1993}. (a) A block diagram showing the ring gantry in a traditional tomotherapy unit.  }
+	\includegraphics[width=\linewidth]{fig1}
+  \label{fig1}
+  \caption{A traditional tomotherapy unit, Ref \cite{Mackie1993}. (a) A block diagram showing the ring gantry, and the radiation source}
   \end{figure*}
+	%----------------------------------
+	% References
+  %----------------------------------
+
+  \bibliography{Paper}{}
+  \bibliographystyle{IEEEtran}
 

### 2014-12-01 BME 560/Paper.tex
Basic Structure

@@
 \begin{document}
-  \markboth{BME 560 Medical Imaging: X-ray, CT, and Nuclear Methods. Fall, 2014}%
+  \markboth{BME 560 Medical Imaging: X-ray, CT, and Nuclear Methods. Fall, 
+  2014}%
   {BME 560 Medical Imaging: X-ray, CT, and Nuclear Methods. Fall, 2014}
@@
   \author{Rahul Krishna, 
-  \IEEEauthorblockA{\normalsize {\textit{Dept. of Electrical and Computer Engineering}\\
-    North Carolina State University, Email: \href{mailto:rkrish11@ncsu.edu}{{rkrish11@ncsu.edu}}}}}
+  \IEEEauthorblockA{\normalsize {\textit{Dept. of Electrical and Computer 
+  Engineering}\\
+    North Carolina State University, Email: 
+    \href{mailto:rkrish11@ncsu.edu}{{rkrish11@ncsu.edu}}}}}
 
@@
   \begin{abstract}
-    Tomotherapy is a form of 3D-conformal radiotherapy which involves the delivery of intensity modulated radiation therapy (IMRT) using rotational fan beam in a manner quite similar to that seen in modern CT scanners.
-The modern tomotherapy systems have a couch and gantry which are in continuous motion, closely resembeling the traditional helical-CT systems.
-This kind of radiotherapy is hence called helical tomotherapy.
-Helical tomotherapy delivers IMRT based on the images of the patient in the treatment position, and these systems do this by acquiring CT images of the patient.
-This paper is a discourse on the current state-of-the-art in the field, foucsing primarily the technique's conceptual working and results of its clinical implementation.
+    Tomotherapy is a form of 3D-conformal radiotherapy which involves the 
+    delivery of intensity modulated radiation therapy (IMRT) using rotational 
+    fan beam in a manner quite similar to that seen in modern CT scanners. The 
+    modern tomotherapy systems have a couch and gantry which are in continuous 
+    motion, closely resembeling the traditional helical-CT systems. This kind 
+    of radiotherapy is hence called helical tomotherapy. Helical tomotherapy 
+    delivers IMRT based on the images of the patient in the treatment position, 
+    and these systems do this by acquiring CT images of the patient. This paper 
+    is a discourse on the current state-of-the-art in the field, foucsing 
+    primarily the technique's conceptual working and results of its clinical 
+    implementation.
 
@@
   \section{Introduction}
-	\IEEEPARstart{T}{he} past couple of decades have seen tremendous advances in radiation oncology.
-The advent of faster and smaller computers has helped transform the field of radiation therapy and treatment planning.
-The term tomotherapy translates to ``slice therapy'', and it is derived from tomography.
-The system is designed to make use of the tomographic reconstruction mathematics for treatment and also for verification.
-The idea was conceived to tackle several major issues that plagued radiation oncology.
-One of the primary issues was the limitation of target dose that can be delivered due to the presence of neighboring sensitive sturctures.
-One of the potential solutions to avoiding this was to make use of multiple radiation beams with non-uniform beam intensities.
-This method allows us to conform the radiation to the target region thereby sparing the sensitive normal structures which would otherwise prevent normal dose delivery to the affected region.
+	\IEEEPARstart{T}{he} past couple of decades have seen tremendous advances in 
+	radiation oncology. The advent of faster and smaller computers has helped 
+	transform the field of radiation therapy and treatment planning. The term 
+	tomotherapy translates to ``slice therapy'', and it is derived from 
+	tomography. The system is designed to make use of the tomographic 
+	reconstruction mathematics for treatment and also for verification. The idea 
+	was conceived to tackle several major issues that plagued radiation oncology. 
+	One of the primary issues was the limitation of target dose that can be 
+	delivered due to the presence of neighboring sensitive sturctures. One of the 
+	potential solutions to avoiding this was to make use of multiple radiation 
+	beams with non-uniform beam intensities. This method allows us to conform the 
+	radiation to the target region thereby sparing the sensitive normal 
+	structures which would otherwise prevent normal dose delivery to the affected 
+	region.
 
-  The setup has a linear accelerator mounted on a rotating gantry as seen in CT sacnners.
-The radiation is delivered to a patient in a helical way, obtained by concurrent gantry rotation and couch/patient travel as shown in Fig.
-\ref{fig1}.
-In general, the helical tomotherapy units have significantly different radiation fields when compared to other radiotherapy systems.
-This difference can be owed to the absence of absence of a flattening filter, a thin target, an electron stopper, a beam hardener and a compact primary collimator.
-And for this reason, this paper will briefly highlight the radiation characteristics of the helical tomotherapy unit, especially in parts where it differs from standard accelerators.
+  Tomotherapy was designed in the University of Wisconsin - Madison and 
+  TomoTherapy Inc., Madison, WI. The first prototype investigated in this study 
+  was installed at University of Wisconsin Hospital and Clinics in Madison, WI, 
+  USA. 
+  The setup has a linear accelerator mounted on a rotating gantry as seen in CT 
+  sacnners. The radiation is delivered to a patient in a helical way, obtained 
+  by concurrent gantry rotation and couch/patient travel as shown in Fig. 
+  \ref{fig1}. In general, the helical tomotherapy units have significantly 
+  different radiation fields when compared to other radiotherapy systems. This 
+  difference can be owed to the absence of absence of a flattening filter, a 
+  thin target, an electron stopper, a beam hardener and a compact primary 
+  collimator. And for this reason, this paper will briefly highlight the 
+  radiation characteristics of the helical tomotherapy unit, especially in 
+  parts where it differs from standard accelerators.
   \begin{figure*}[t!]
@@
   \label{fig1}
-  \caption{A traditional tomotherapy unit, Ref \cite{Mackie1993}. (a) A block diagram showing the ring gantry, and the radiation source}
+  \caption{A traditional tomotherapy unit, Ref \cite{Mackie1993}. (a) A block 
+  diagram showing the ring gantry, and the radiation source}
   \end{figure*}
@@
 
+  \section{Methods and Materials}
+  \subsection{Construction}
+  \subsubsection{A note on Serial Tomotherapy}
+  \subsection{Radiation Characteristics}
+  \subsection{Comparisions between other conformal therapy techniques}
+  \section{Clinical Results}
+  \subsection{Whole brain helical Tomotherapy}
+  \subsection{Inoperable Lung Cancer}
+  \subsection{Rectal Cancer}
+
   \bibliography{Paper}{}

### 2014-12-01 BME 560/Paper.tex
Introduction updated

@@
   was installed at University of Wisconsin Hospital and Clinics in Madison, WI, 
-  USA. 
+  USA. The first paper on tomotherapy was submitted in 1992, Ref. 
+  \cite{Mackie1993}. This paper described most of the details seen in the 
+  modern sytems in use today. This paper also introducted the idea of using a 
+  continuously moving slip-ring gantry. The usage of fan-beam to form a 
+  modulating beam, and a temorally modulating collimator assembly (this came 
+  to be known as the `Binary Collimator').
+
   The setup has a linear accelerator mounted on a rotating gantry as seen in CT 

### 2014-12-02 BME 560/Paper.tex
Introduction updated
More updates

--- 2014-12-01 BME 560/Paper.tex
@@
-\documentclass[12pt,journal,compsoc]{IEEEtran} %draftclsnofoot, 
+\documentclass[10pt,journal,compsoc]{IEEEtran} %draftclsnofoot, 
 \usepackage{graphicx}
@@
 \setlength\fboxrule{1pt}
+\usepackage{multicol}
+\usepackage{bigstrut}
+\usepackage{tabularx}
+\usepackage{tabulary}
+\usepackage{booktabs}
 \usepackage{amsmath}
@@
 	tomotherapy translates to ``slice therapy'', and it is derived from 
-	tomography. The system is designed to make use of the tomographic 
-	reconstruction mathematics for treatment and also for verification. The idea 
-	was conceived to tackle several major issues that plagued radiation oncology. 
-	One of the primary issues was the limitation of target dose that can be 
-	delivered due to the presence of neighboring sensitive sturctures. One of the 
-	potential solutions to avoiding this was to make use of multiple radiation 
-	beams with non-uniform beam intensities. This method allows us to conform the 
-	radiation to the target region thereby sparing the sensitive normal 
-	structures which would otherwise prevent normal dose delivery to the affected 
-	region.
+	tomography. Tomotherapy is a form of 3D Conformal Radiotherapy (3D-CRT), 
+  which aims to conform the spatial distribution of the prescribed dose to a 
+  target volume. The volume includes the cancerous cells plus a margin for 
+  spatial uncertainties. While doing do it tries to minimize the dose to the
+  surrounding normal structures. The tomotherapy system is designed to make use 
+  of the tomographic 	reconstruction mathematics for treatment and also for 
+  verification. The idea 	was conceived to tackle several major issues that 
+  plagued radiation oncology. One of the primary issues was the limitation of 
+  target dose that can be 	delivered due to the presence of neighboring 
+  sensitive sturctures. One of the 	potential solutions to avoiding this was 
+  to make use of multiple radiation 	beams with non-uniform beam intensities. 
+  This method allows one to conform 	the radiation to the target region 
+  thereby   sparing the sensitive normal 	structures which would otherwise 
+  prevent   normal dose delivery to the affected 	region, see Fig. \ref{intro}.
 
-  Tomotherapy was designed in the University of Wisconsin - Madison and 
-  TomoTherapy Inc., Madison, WI. The first prototype investigated in this study 
-  was installed at University of Wisconsin Hospital and Clinics in Madison, WI, 
-  USA. 
-  The setup has a linear accelerator mounted on a rotating gantry as seen in CT 
+  The setup has a 
+  linear accelerator mounted on a rotating gantry as seen in CT 
   sacnners. The radiation is delivered to a patient in a helical way, obtained 
@@
   thin target, an electron stopper, a beam hardener and a compact primary 
-  collimator. And for this reason, this paper will briefly highlight the 
+  collimator. This paper will briefly highlight the 
   radiation characteristics of the helical tomotherapy unit, especially in 
   parts where it differs from standard accelerators.
+
+  The rest of this paper is 
+  organized as follows. Section \ref{history} talks 
+  about the history of tomotherapy. Section \ref{methods} has 3 subsections: 
+  \ref{construction} talks about the construction of the tomotherapy unit, 
+  \ref{radiation} discusses the radiation characteristics of helical 
+  tomotherapy, and \ref{comparisions} brielfy examines the differences between 
+  this techique and other conformal therapy techniques. Section \ref{clinical} 
+  is a collection of some clinical results where tomotherapy has been, and has 
+  not been, effective. Finally, section \ref{conclusions} presents concluding 
+  remarks on the the topic.
+
+  \begin{figure}[htbp!]
+    \includegraphics[width=\linewidth]{intro}
+    \label{intro}
+    \caption{An example of treatment planning in a modern 3D-CRT. In this 
+    example, a 3D view of the patient, the PTV, spinal cord, and parotid 
+    glands, and the 9 intensity modulated beams used to generate the IMRT dose 
+    distribution can be seen. \textit{Image courtesy \cite{IMRT}}}
+  \end{figure}
+
   \begin{figure*}[t!]
-	\includegraphics[width=\linewidth]{fig1}
-  \label{fig1}
+    \centering
+  \includegraphics[width=0.9\linewidth]{fig1}
   \caption{A traditional tomotherapy unit, Ref \cite{Mackie1993}. (a) A block 
     diagram showing the ring gantry, and the radiation source}
+  \label{fig1}
+
 \end{figure*}
+
+\begin{figure}[htbp!]
+  \centering
+  \includegraphics[width=0.921\linewidth]{fig2}
+  \caption{``Running start-stop'' mechanism as proposed in Ref. 
+    \cite{Mackie1993}. (a)--(c) }
+  \label{fig2}
+
+\end{figure}
 	%----------------------------------
@@
   %----------------------------------
+  \section{History}
+  \label{history}
+  Tomotherapy was designed in the University of Wisconsin - Madison and 
+  TomoTherapy Inc., Madison, WI. The first prototype investigated in this study 
+  was installed at University of Wisconsin Hospital and Clinics in Madison, WI, 
+  USA. The first paper on tomotherapy was submitted in 1992, Ref. 
+  \cite{Mackie1993}. This paper described most of the details seen in the 
+  modern sytems used today. This paper also introducted the idea of using a 
+  continuously moving slip-ring gantry. The usage of fan-beam to form a 
+  modulating beam, and a temorally modulating collimator assembly (this came 
+  to be known as the `Binary Collimator') was also initially proposed in this 
+  paper. It also recommended performing 
+  intensity modulation without the use of a field flattening filter, thus 
+  improving the spectrum across the beam.
+
+  Several initial theories proposed in the paper could not be implemented. For 
+  instance, to address the target cooling issue that is faced in modern photon 
+  beam radiotherapy, the authors proposed engineering a stationary ``hoop'' 
+  target with water supplied cooling; this could not be implemented due to the 
+  increased collimation complexity. Also, in order to give a steep penumbra to 
+  the target region, the authors of the original paper proposed a 
+  ``start-stop'' mechanism where the collimator jaws defining the slice width 
+  would be 
+  close and later on as the patient traverses through the field the opposite 
+  would happen. Fig. \ref{fig2}, taken from Ref. \cite{Mackie1993}, shows how 
+  this was supposed to happen. But, this idea wasn't implementable either, 
+  mainly because the technique required the jaws to be in movement during 
+  treatment, optimization of beams near the ‘bow’ and the ‘stern’ of the 
+  tumour may limit the amount of dose received.
+
+  For a more comprehensive history of this form of radiotherapy the readers 
+  might want to refer to \cite{Mackie2006}.
 
   \section{Methods and Materials}
+  \label{methods}
   \subsection{Construction}
+  \label{construction}
   \subsubsection{A note on Serial Tomotherapy}
   \subsection{Radiation Characteristics}
+  \label{radiation}
   \subsection{Comparisions between other conformal therapy techniques}
+  \label{comparisions}
+    \begin{table*}[htbp]
+      \centering
+      \caption{A comparision between standard and non-standard IMRT delivery 
+      systems (Ref. \cite{Fenwick2006})}
+      \small{
+      \begin{tabulary}{\linewidth}{LLLLLLL}
+        \toprule[0.04cm]
+
+        \textbf{System} & \textbf{Gantry} & \textbf{ Beam Geometry} & 
+        \textbf{Collimated} & \textbf{Modulated} & \textbf{Imaging} & 
+        \textbf{Gating
+          Potential} \\\toprule[0.04cm]
+
+        Conventional linac plus multileaf & C-Arm & Non-coplanar cone beam & 
+        Jaws 
+        with conventional
+        multileaf & Jaws with conventional
+        multileaf & Portal image, fluoroscopy, kvCT, 
+        infrared 
+        reflectors &
+        Breath-hold, 
+        beam trigger, multileaf tracking \bigstrut\\\midrule
+        Conventional linac minus multileaf & C-Arm & Non-coplanar cone beam & 
+        Jaws with/without tertiary attenuator
+        & Jaws with/without tertiary attenuator
+        & Portal image, fluoroscopy, kvCT, infrared 
+        reflectors & Breath-hold,
+        beam trigger,
+        jaw tracking \bigstrut\\\midrule
+        Serial tomotherapy & C-Arm & Fanbeam, coplanar, sequential,
+        indexed trajectory & Jaws with binary
+        multileaf & Binary multileaf & Portal image, 
+        fluoroscopy, kvCT, infrared reflectors & Breath-hold
+        during each
+        slice \bigstrut\\\midrule
+        Helical tomotherapy & Ring  &  Fanbeam,
+        coplanar, helical
+        trajectory & Jaws with binary
+        multileaf & Binary multileaf & MVCT, infrared 
+        reflectors & Delivery
+        synchronized
+        with breathing
+        cycle \bigstrut \\\midrule
+        Robotic linac & Robotic Arm &  Pencil-beam,
+        noncoplanar & Circular collimator & Superposition of pencilbeams by 
+        robotic arm & Biplanar radiography, infrared 
+        reflectors & Beam 
+        trigger,
+        robotic
+        tracking \bigstrut \\
+        \bottomrule
+      \end{tabulary}}%
+
+      \label{tab:addlabel}%
+    \end{table*}%
   \section{Clinical Results}
+  \label{clinical}
+  \subsection{Total Body Irradiation (TBI)}
   \subsection{Whole brain helical Tomotherapy}
@@
   \subsection{Rectal Cancer}
-
+  \section{Conclusion}
+  \label{conclusions}
   \bibliography{Paper}{}

### 2014-12-02 BME 560/rmAux.sh

@@ -1,0 +1,2 @@
+#!/bin/bash
+rm *.aux *.blg *.log *.out *.synctex.gz *.bbl

### 2014-12-02 BME 560/Paper.tex
Updates

@@
 \setlength{\parskip}{1em}
+\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
 \usepackage{hyperref}
@@
     \centering
-  \includegraphics[width=0.9\linewidth]{fig1}
+  \includegraphics[width=0.89\linewidth]{fig1}
   \caption{A traditional tomotherapy unit, Ref \cite{Mackie1993}. (a) A block 
@@
   \centering
-  \includegraphics[width=0.921\linewidth]{fig2}
+  \includegraphics[width=0.9\linewidth]{fig2}
   \caption{``Running start-stop'' mechanism as proposed in Ref. 
@@
 
-  For a more comprehensive history of this form of radiotherapy the readers 
-  might want to refer to \cite{Mackie2006}.
+  For a more comprehensive history the readers might want to refer to 
+  \cite{Mackie2006}. The paper talks about the how this idea was 
+  conceived and other technological advances led to its current state.
 
@@
   \label{methods}
+  This section briefly discribes various aspects of helical tomography ranging 
+  from it's construction and it's radiation characteristics to the differences 
+  between it and other IMRT techniques.
+
   \subsection{Construction}
+  \begin{figure}
+    \centering
+    \subfloat[\label{fig4a}][A simplified view of the Helical Tomotherapy 
+    treatment head system in use today. The setup consists of a 6 MV linac to 
+    produce an x-ray beam which is collimated down to a fan-beam using 2 
+    moveable jaws (denoted as `y-jaws' in the image)]{
+      \includegraphics[width=\linewidth]{fig4}}\\
+    \subfloat[][]{
+      \includegraphics[width=\linewidth]{fig5}}
+
+  \end{figure}
   \label{construction}
@@
   \label{radiation}
-  \subsection{Comparisions between other conformal therapy techniques}
+  \subsection{Comparisions between IMRT techniques}
   \label{comparisions}
-    \begin{table*}[htbp]
+    \begin{table*}[htbp!]
       \centering
@@
 
-      \label{tab:addlabel}%
+      \label{tab:compare}%
     \end{table*}%
+  Tomotherapy is different from other standard IMRT techiniques such as 
+  conformal radiotherapy (CRT) techniques and non-standard IMRT techniques like 
+  Cyber knife.   Standard CRT techniques generate highly conformal radiotherapy 
+  using radiation fields generated in a few fixed-angle positions. These are 
+  generated by linear accelerators (aka. LINAC) which are then modulated by 
+  conventional leaf collimators operated in either dynamic mode or the standard 
+  step-and-shoot mode. CyberKnife is a modern radiotherapy system developed by 
+  Accuray, Inc., primarily for radiosurgery. It makes use of a highly precise 
+  robotic arm to delivery the doses. The arm is computer driven to achieve very 
+  high precision, it is mounted with a compact 6-MV LINAC whose orientation is 
+  determined by 6 different mechanical subsystems. This robotic arm can be 
+  moved with a much greater generality than most conventional sytsems. Table 
+  \ref{tab:compare} highlights the key differences in various systems. For the 
+  sake the completeness, the authors of Ref. \cite{Fenwick2006} have 
+  dicotomized the conventional system into 2 types, with and without a 
+  multileaf collimator, and the tomotherapy into serial and parallel 
+  tomotherapy.
   \section{Clinical Results}

### 2014-12-02 BME 560/Paper.tex
Updates..

@@
   \subsection{Construction}
+  \label{construction}
   \begin{figure}
     \centering
-    \subfloat[\label{fig4a}][A simplified view of the Helical Tomotherapy 
-    treatment head system in use today. The setup consists of a 6 MV linac to 
-    produce an x-ray beam which is collimated down to a fan-beam using 2 
-    moveable jaws (denoted as `y-jaws' in the image)]{
-      \includegraphics[width=\linewidth]{fig4}}\\
     \subfloat[][]{
-      \includegraphics[width=\linewidth]{fig5}}
-
+      \includegraphics[width=\linewidth]{fig5}
+      \label{fig4a}}\\
+    \subfloat[][]{
+      \includegraphics[width=\linewidth]{fig4}
+      \label{fig4b}}
+    \caption{\protect\subref{fig4a} Axial rotation of the fan beam as the 
+      patient (represented 
+      as a cylinder) traverses laterally (Along the y-axis). 
+      \protect\subref{fig4b} A simplified view of the Helical 
+      Tomotherapy 
+      treatment system (at a gantry angle of 0$^\circ$) in use today. The 
+      setup consists of a 6 MV linac to produce an x-ray beam which is 
+      collimated down to a fan-beam using 2 moveable jaws (denoted as `y-jaws' 
+      in the image). There is also a Binary Multileaf to modulate the beam 
+      laterally. \textit{Image  
+      courtesy of \cite{Fenwick2004}}}
+    \label{fig4}
   \end{figure}
-  \label{construction}
+  Figure \ref{fig4} show the basics of dose delivery in the helical tomotherapy 
+  system. There is a short in-line 6 MV linear accelerator that rotates on a 
+  ring gantry at a source-axis of 85 cms (instead of the usual 100 cms). The 
+  patient couch is translated through the gantry bore in the y-direction as 
+  shown in \ref{fig4}\protect\subref{fig4a}. The pitch is about 0.2 to 0.5 
+  (Pitch is the distance traveled by the couch in one rotation, divided by the 
+  field width in the direction of traversal). The pair of y-jaws in 
+  \ref{fig4}\protect\subref{fig4b} are used to define the y-width of the beam. 
+  These are usually preset to values like 1,2.5, or 5 cm before imaging. 
+  Lateral modulation of the beam is achieved using the binary multileaf. This 
+  system consists of 64 binary multileaves, each having a width of 6.25 mm 
+  projecting onto an isocenter. These leaves transition rapidly between on 
+  and off states, the duration of which is made use of to modualate the 
+  intensity. 
   \subsubsection{A note on Serial Tomotherapy}

### 2014-12-08 BME 560/Paper.tex
Stuff added

--- 2014-12-02 BME 560/Paper.tex
@@
   this techique and other conformal therapy techniques. Section \ref{clinical} 
-  is a collection of some clinical results where tomotherapy has been, and has 
-  not been, effective. Finally, section \ref{conclusions} presents concluding 
-  remarks on the the topic.
+  is a collection of some clinical applications where tomotherapy 
+  has, and in some cases has not,  been effective. Finally, section 
+  \ref{conclusions} presents concluding 
+  remarks on the topic.
 
@@
   \subsection{Construction}
+  \label{construction}
   \begin{figure}
     \centering
-    \subfloat[\label{fig4a}][A simplified view of the Helical Tomotherapy 
-    treatment head system in use today. The setup consists of a 6 MV linac to 
-    produce an x-ray beam which is collimated down to a fan-beam using 2 
-    moveable jaws (denoted as `y-jaws' in the image)]{
-      \includegraphics[width=\linewidth]{fig4}}\\
     \subfloat[][]{
-      \includegraphics[width=\linewidth]{fig5}}
+      \includegraphics[width=\linewidth]{fig5}
+      \label{fig4a}}\\
+    \subfloat[][]{
+      \includegraphics[width=\linewidth]{fig4}
+      \label{fig4b}}
+    \caption{\protect\subref{fig4a} Axial rotation of the fan beam as the 
+      patient (represented 
+      as a cylinder) traverses laterally (Along the y-axis). 
+      \protect\subref{fig4b} A simplified view of the Helical 
+      Tomotherapy 
+      treatment system (at a gantry angle of 0$^\circ$) in use today. The 
+      setup consists of a 6 MV linac to produce an x-ray beam which is 
+      collimated down to a fan-beam using 2 moveable jaws (denoted as `y-jaws' 
+      in the image). There is also a Binary Multileaf to modulate the beam 
+      laterally. \textit{Images courtesy of \cite{Fenwick2004}}}
+    \label{fig4}
+  \end{figure}
+  Figure \ref{fig4} show the basics of dose delivery in the helical tomotherapy 
+  system. There is a short in-line 6 MV linear accelerator that rotates on a 
+  ring gantry at a source-axis of 85 cms (instead of the usual 100 cms). The 
+  patient couch is translated through the gantry bore in the y-direction as 
+  shown in \ref{fig4}\protect\subref{fig4a}. The pitch is about 0.2 to 0.5 
+  (Pitch is the distance traveled by the couch in one rotation, divided by the 
+  field width in the direction of traversal). The pair of y-jaws in 
+  \ref{fig4}\protect\subref{fig4b} are used to define the y-width of the beam. 
+  These are usually preset to values like 1,2.5, or 5 cm before imaging. 
+  Lateral modulation of the beam is achieved using the binary multileaf. This 
+  system consists of 64 binary multileaves, each having a width of 6.25 mm 
+  projecting onto an isocenter. These leaves transition rapidly between on 
+  and off states, the duration of which is made use of to modualate the 
+  intensity. Other parameters are tabulated in \ref{tab1}.
+  % Table generated by Excel2LaTeX from sheet 'Sheet1'
+  \begin{table}[t]
+    \centering
+    \caption{Helical Tomotherapy Characteristics}
+    \begin{tabularx}{1\linewidth}{XX}
+      \toprule[0.3mm]
+      \textbf{Parameter} & \textbf{Value} \\
+      \midrule
+      Gantry Rotation angle & 
+      7\textsuperscript{$\circ$} \\
+      Projections per revolution & 51 \\
+      Rotation velocity & 10 - 60 sec/rotation \\
+      Time-per projection & $>$ 196 ms \\
+      \bottomrule
+    \end{tabularx}%
+    \label{tab1}%
+  \end{table}%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             
+  \begin{figure*}[htbp]
+    \centering
+    \subfloat[][]{
+      \includegraphics[width=0.5 \linewidth]{fig6}
+      \label{radchara}}
+    \subfloat[][]{
+      \includegraphics[width=0.5 \linewidth]{fig7}
+      \label{radcharb}}
+    \caption{\protect\subref{radchara} Shows the photon fluence profile of the 
+    tomotherapy treatment beam. Notice the characteristic conical shape of the 
+    tomotherapy profile (solid red line) and the flat shape of the conventional 
+    linac IMRT system (dashed blue line). 
+    \protect\subref{radcharb} Average photon beam spectra of the helical 
+    tomography system in two operational modes: imaging (dashed green) and 
+    treatment mode (solid red). \textit{Image courtesy of \cite{Jeraj2004}}}
+    \label{fig5}
+  \end{figure*}
+  \subsubsection{A note on Serial Tomotherapy}
+  Serial tomography is another variant of tomotherapy that has been in use for 
+  sometime now. The first clinical implementation occured as early as 1994. The 
+  setup consists of a binary multileaf collimator attached to a conventional 
+  linear accelerator. The collimator comprises of two opposing banks of 20 
+  tungsten leaves which are driven pneumatically to lie either within or just 
+  outside the fan beam radiation. The fan beam itself is modified by arranging 
+  the leaves to lie within the radiation field for a variable amount of time.
 
-  \end{figure}
-  \label{construction}
-  \subsubsection{A note on Serial Tomotherapy}
+  This can also be achieved by slightly modifying the conventional linear 
+  accelerator by adding a binary multileaf collimator to the head of the linac. 
+  Axial tomotherapy dose distributions are delivered slice-by-slice, with 
+  patients being sequentially and discretely translated through the linac 
+  gantry rotational plane between slices, helical distributions are delivered 
+  without interruptions; patients are translated smoothly through the bore of 
+  the machine as its gantry continuously and synchronously rotates, the 
+  therapy equivalent of spiral computed tomography \cite{Fenwick2006}. 
   \subsection{Radiation Characteristics}
   \label{radiation}
+  This section aims to briefly highlight the key differences in radiation 
+  characteristics of helical tomography and other forms of radiotherapy. One of 
+  the key differences is the lack of flattening filter, which makes the dose 
+  more uniform are greater depths. As a result of this, the photon fluence 
+  profile is shaped differently when compared to a traditional radiotherapy 
+  system, as can be seen in Fig. \ref{radchara}. The conical shape of the 
+  profile implies that there will be an increased average dose rate and thus 
+  reduces the imaging time.
+
+  Figure \ref{radcharb} shows the differences in the photon spectrum between 
+  the 
+  treatment and imaging modes of helical tomotherapy. Notice that the in the 
+  imaging mode the spectrum has a lower energy when compared to treatment mode; 
+  this is done so as to obatin better images by improving the contrast. A more 
+  comprehensive comparision is documented in Ref. \cite{Jeraj2004}
+
   \subsection{Comparisions between IMRT techniques}
   \label{comparisions}
-    \begin{table*}[htbp!]
+    \begin{table*}[t!]
       \centering
@@
         \toprule[0.04cm]
-
         \textbf{System} & \textbf{Gantry} & \textbf{ Beam Geometry} & 
@@
   determined by 6 different mechanical subsystems. This robotic arm can be 
-  moved with a much greater generality than most conventional sytsems. Table 
-  \ref{tab:compare} highlights the key differences in various systems. For the 
+  moved with a much greater generality than most conventional sytsems.
+
+  Table \ref{tab:compare} highlights the key differences in various systems. 
+  For the 
   sake the completeness, the authors of Ref. \cite{Fenwick2006} have 
@@
   tomotherapy.
-  \section{Clinical Results}
+  \section{Clinical Applications}
   \label{clinical}
+  This section highlights few of the many clinical applications of tomotherapy. 
   \subsection{Total Body Irradiation (TBI)}
+  Tomotherapy can be used in establishing total body irradiation (TBI) to gain 
+  greater control over the dose distribution and to spare organs that may be at 
+  risk.
+
+  One of the disadvantages of using Helical Tomography (HT) for TBI is that it 
+  can't be used when the body length of the patient exceeds 145 cms. For 
+  patients who are taller than this, a better solution needs to be deviced.
   \subsection{Whole brain helical Tomotherapy}

### 2014-12-08 BME 560/Paper.tex
Updates

@@
   greater control over the dose distribution and to spare organs that may be at 
-  risk.
+  risk. It was shown in Ref. \cite{Gruen2013} that using HT provided excellent 
+  conformal 
+  lung sparing with mean doses not exceeding 10 Gy. No lung toxicity was 
+  observed for over 15 months after follow-up. Also, the overall morbidity 
+  during the treatment period was very low, corresponding to grades 1-2 side 
+  effects.
 
-  One of the disadvantages of using Helical Tomography (HT) for TBI is that it 
-  can't be used when the body length of the patient exceeds 145 cms. For 
+  In general the use of HT was effective in that it provided excellent 
+  individual sparing of organs and very little side effects. There are still 
+  room for improvements as one of the disadvantages of using Helical Tomography 
+  (HT) for TBI is that it 
+  can't be used when the body length of the patient exceeds 145 cms. Although 
+  this makes it very effective in cases of pediatric oncology, for 
   patients who are taller than this, a better solution needs to be deviced.
+
   \subsection{Whole brain helical Tomotherapy}

### 2014-12-09 BME 560/Paper.tex
Almost done

@@
 \usepackage{multicol}
+\bstctlcite{IEEEexample:BSTcontrol}
 \usepackage{bigstrut}
@@
 \usepackage{amsmath}
+\usepackage{balance}
+\usepackage{flushend}
 \setlength{\parindent}{0em}
@@
   different radiation fields when compared to other radiotherapy systems. This 
-  difference can be owed to the absence of absence of a flattening filter, a 
+  difference can be owed to the absence of a flattening filter, a 
   thin target, an electron stopper, a beam hardener and a compact primary 
@@
     \begin{tabularx}{1\linewidth}{XX}
-      \toprule[0.3mm]
+      \toprule[0.4mm]
       \textbf{Parameter} & \textbf{Value} \\
-      \midrule
+      \midrule[0.4mm]
       Gantry Rotation angle & 
@@
   this is done so as to obatin better images by improving the contrast. A more 
-  comprehensive comparision is documented in Ref. \cite{Jeraj2004}
+  comprehensive comparision is documented in Ref. \cite{Jeraj2004}.
 
@@
       \label{tab:compare}%
-    \end{table*}%
+    \end{table*}% \be
   Tomotherapy is different from other standard IMRT techiniques such as 
@@
   greater control over the dose distribution and to spare organs that may be at 
-  risk. It was shown in Ref. \cite{Gruen2013} that using HT provided excellent 
-  conformal 
-  lung sparing with mean doses not exceeding 10 Gy. No lung toxicity was 
-  observed for over 15 months after follow-up. Also, the overall morbidity 
-  during the treatment period was very low, corresponding to grades 1-2 side 
-  effects.
+  risk. In a study conducted by Ref. \cite{Gruen2013}, with a cohort of 10 
+  patients aged 4 - 22 years with acute lymphoblastic or myeloic leukemia, it 
+  was shown that, among other benifits, using HT provided excellent 
+  conformal lung sparing with mean doses not exceeding 10 Gy. No lung toxicity 
+  was observed for over 15 months after follow-up. Also, the overall 
+  morbidity   during the treatment period was very low, corresponding to grades 
+  1-2 side   effects. Table \ref{tbi_side} from Ref. \cite{Gruen2013} documents 
+  other side  effects, notice that none of the side effects for any patient 
+  were of grades 3 or 
+  4.
+
+  \begin{table}[t]
+    \caption{Acute Toxicity (Ref. \cite{Gruen2013})}
+    \centering
+    \includegraphics[width=\linewidth]{fig8.png}
+    \label{tbi_side}
+  \end{table}
 
@@
   \subsection{Whole brain helical Tomotherapy}
+  Whole brain helical tomotherapy is a possible treatment option for patients 
+  suffering from malignant melanoma with four or more brain metastates. The 
+  possiblity of integrated boost with enhanced hippocampal sparing makes the 
+  use of HT a very reliable approach.
+
+  A study conducted by Ref. \cite{Gondi2010} showed that Helical 
+  tomotherapy 
+  spared the hippocampus, with a median dose of 5.5 Gy and maximum 
+  dose of 12.8 
+  Gy. Other linear accelerator based IMRT spared the hippocampus, 
+  with a median 
+  dose of 7.8 Gy and maximum dose of 15.3 Gy. On a per-fraction 
+  basis, mean 
+  dose to the hippocampus (normalized to 2-Gy fractions) was reduced 
+  by 87\% to 
+  0.49 Gy2 using helical tomotherapy and by 81\% to 0.73 Gy2 using 
+  LINAC-based 
+  IMRT. Target coverage and homogeneity was acceptable with both IMRT 
+  modalities, with differences largely attributed to more rapid dose 
+  falloff 
+  with helical tomotherapy.
+
+  Another study was conducted by Ref. \cite{Hauswald2013} to explore 
+  and 
+  compare the 
+  effects of treatment and response to conventional radiotherapy with 
+  a 30 Gy 
+  dose in 10 fractions and a standard helical tomography with 30 Gy 
+  dose, 10 
+  fraction, integrated boost of 50 Gy at the regions of metastates 
+  with a 
+  hippocampal-sparing. This study showed that the even though HT 
+  produced 
+  excellent homogeneity and conformality with integrated boost, it 
+  still has 
+  some limitations when compared to classical radiotherapy on account 
+  of the 
+  fact that all HT plans had a higher dose brain exposure. The 
+  effects 
+  shouldn't be too much of an issue as the total treatment time is 
+  lower, and 
+  so too the integral dose, due to the dynamic couch setup and other 
+  design 
+  aspects of the HT system.
   \subsection{Inoperable Lung Cancer}
-  \subsection{Rectal Cancer}
+  Radiation therapy has become a standard treatment protocol for 
+  patients 
+  suffering from non-small cell lung cancer and other solitary lung 
+  metastatis. 
+  The use had been quite controversial. Among other things, the 
+  primary 
+  concerns were the expansion of the low-dose irradiated lung volume 
+  resulting 
+  from the coplanar beam delivery and uncertainity in dose 
+  distribution due to 
+  respiration.
+
+  However, a very recent study published by Ref. \cite{Nagai2014} seem 
+  to show 
+  that Helical Tomotherapy for lung cancer is both safe and 
+  effective. In this 
+  study 2 groups of lung tumor patients were treated; one group of 37 
+  patients 
+  were administered a dose of 48 Gy in 4 fractions and another group 
+  of 35 
+  patients were administered a dose of 50-60 Gy in 5-8 fractions. The 
+  4-fraction group had a median planning target volume (PTV) of 6.9 
+  cm\textsuperscript{3} and the 5-8 fraction group had a median PTV 
+  of 14 
+  cm\textsuperscript{3}. The study reports that only 2 of the 37 and 
+  2 out of 
+  35 patients in the 4-fraction cohort respectively had Grade-2 
+  radiation 
+  pneumonitis. No other complications were reported.
+
+  \subsection{Colorectal Cancer}
+  A study published by Ref. \cite{Yu2013} showed that using 
+  tomotherapy 
+  could produce acceptable coverage for the target while decreasing 
+  the mean dose to sensitive surrounding areas such as bowel, bladder 
+  and femur heads. They report that while tomotherapy had a  lower 
+  radical 
+  dose homogeneity index (rHDI) compared to conventional 3D conformal 
+  radiotherapy (3D-CRT) (0.7$\pm$0.01 vs 22.05$\pm$2.76, p$<$0.001),  
+  it did significantly reduced the volume of sensitive tissues 
+  receiving a large dose; this was measured using $V_{nGy}$, which 
+  denotes the percentage of volume receiving a dose greater than n 
+  Gy. Figure \ref{fig6}, taken from \cite{Yu2013}, shows the dose 
+  reduction 
+  acheived by tomotherapy.
+  \begin{figure}[t]
+		\centering
+    \includegraphics[width=\linewidth]{fig9.png}
+    \caption{Tomotherapy(dashed blue line) significantly reduce 
+    $V_{nGy}$ for the bowel as compared to 3D-CRT (with p<0.001) for 
+    all doses except at 5 Gy (p = 0.568), Ref. \cite{Yu2013}.}
+  	\label{fig6}
+  \end{figure}
+
+  \subsection{Arteriovenous Malformations}
+  Arteriovenous malformations (AVM) are aberrant fistulous connections between 
+  arteries and veins bypassing the normal capillary bed. It occurs in 0.2-0.8\% 
+  of the normal population. If untreated cerebral AVMs can cause hemorrhage and 
+  subsequent neurological impairments. An attempt was made by Ref. 
+  \cite{Krause2013} to 
+  validate the performance of modern tomotherapy systems in tackling AVM.
+
+  They 
+  reported that there were no significant results to show that tomotherapy 
+  outperforms the conventional linac based methods. In fact, as previously 
+  reported by many researchers, tomotherapy exposed bigger brain volumes 
+  to doses $\ge60\%$ of the prescription dose (average 12.75 Gy), albeit only 
+  for a short amount of time. This does, unfortunately, pose risks of 
+  permanent postradiosurgery sequelae influenced by the localisation and the 
+  volume of brain receiving 12 Gy or more. However, these were only theoretical 
+  planning comparison to explore the potential of these methods for small 
+  volume radiosurgery. HT radiosurgery might yet be beneficial for AVM with 
+  special geometry as well as for patients with brain metastases that benefit 
+  from shorter treatment times at the cost of a slightly higher brain exposure.
+
   \section{Conclusion}
   \label{conclusions}
+  In conclusion, IMRT with helical tomotherapy is an advanced form of 
+  radiotherapy which constantly outperforms several conventional 3D-CRT. It 
+  represents one of the most important technical advances in radiation therapy 
+  since the advent of medical linear accelerator.
+
+  Current helical tomography systems provide excellent target volume 
+  conformality while significantly reduction exposure to the surrounding 
+  sensitive tissue. This aspect of the tomotherapy system has motivated its use 
+  in oncology. Some clincal applications are listed above, this list by no 
+  means exhaustive. However, it needs to be mentioned that the results are 
+  reported for small cohorts and in many cases reports are only feasibility 
+  studies. There is a lot active research in the field and as Ref. 
+  \cite{Beavis2004} 
+  suggests, helical tomotherapy can be \textit{a} future of IMRT if not 
+  \textit{the} future.
+
   \bibliography{Paper}{}

### 2015-01-06 Independent Study '15/Proposal/Independent Study Proposal.tex
Independent study proposal

\documentclass{article}
\usepackage{tgbonum}
\usepackage{graphicx}
\usepackage{fullpage}
\begin{document}
% Title Space
\title{Independent Study Proposal}
\author{Rahul Krishna}
\maketitle

% Abstract
\section{Abstract}
This independent study aims to explore the application of multidimensional 
prediction systems in predicting the defects in unseen data. The study proposes 
the use of contrast sets as a planner in order to help understand what changes 
are to be made to mitigate these defects. The efficacy of these changes will 
then be evaluated by using one of several established predictors, such as 
random forest, CART, logistic regression, and so on. The system consists of two 
phases-- Planning and Prediction. A flow chart of the proposed system is shown 
in Fig. \ref{fig1}.

\begin{figure}[h!]
\centering
\includegraphics[width = 0.7\linewidth]{flowchart}
\caption{Flowchart of the proposed defect prediction system.}
\label{fig1}
\end{figure}

\noindent In the planning phase we use training data with recursive 
\textit{FASTMAP} clustering to create create clusters. For a test data, we 
generate contrast sets to indicate changes to be made to reduce defects. In the 
prediction phase, we implement these changes and 
\end{document}

### 2015-01-24 Independent Study '15/Proposal/Independent Study Proposal.tex
Stuff for latex on sublime text, bash scripts and such

@@
-\documentclass{article}
-\usepackage{tgbonum}
+\documentclass[10pt]{article}
+\usepackage{times}
 \usepackage{graphicx}
+\usepackage{hyperref}
+\hypersetup{colorlinks,breaklinks,
+            urlcolor=[rgb]{0,0,1},
+            citecolor=[rgb]{0,0,1},
+            linkcolor=[rgb]{0,0,01}}
 \usepackage{fullpage}
+\setlength{\parindent}{0em}
+\setlength{\parskip}{1em}
+
 \begin{document}
 % Title Space
-\title{Independent Study Proposal}
-\author{Rahul Krishna}
-\maketitle
+\section*{\centering \LARGE \textsc{Independent Study Proposal}}
+%\subsection*{\centering \large \textit{Rahul Krishna}}
 
 % Abstract
-\section{Abstract}
+\subsection*{Abstract}
 This independent study aims to explore the application of multidimensional 
@@
 the use of contrast sets as a planner in order to help understand what changes 
-are to be made to mitigate these defects. The efficacy of these changes will 
-then be evaluated by using one of several established predictors, such as 
-random forest, CART, logistic regression, and so on. The system consists of two 
-phases-- Planning and Prediction. A flow chart of the proposed system is shown 
+are to be made to mitigate the defects. The efficacy of these changes will 
+then be evaluated using one of several established predictors in software 
+defect prediction, such as 
+random forest, CART, logistic regression, and so on, as suggested by 
+\cite{lessmann}. The 
+system 
+consists of two 
+phases -- Planning and Prediction. A flow chart of the proposed system is shown 
 in Fig. \ref{fig1}. 
+\begin{figure}[h!]
+\centering
+\begin{minipage}{0.7\textwidth}
+	\centering
+	\includegraphics[width = \linewidth]{flowchart}
+	\caption{Flowchart of the proposed defect prediction system.}
+	\label{fig1}
+\end{minipage}
+\end{figure}
 
 \begin{figure}[h!]
+\begin{minipage}{0.5\textwidth}
+The planning phase uses training data with recursive 
+\textit{FASTMAP} 
+clustering to create a decision tree. For a test data, we generate contrast 
+sets 
+to indicate changes that needs to be made to in order to reduce defects. The 
+prediction phase implements these changes and predicts the defects in the 
+modified data. We would like to study the distribution of defects in the 
+modified 
+data set compared to the raw test dataset and make appropriate improvements to 
+the planning system. Much of the preliminary work was carried out fall 2014 and 
+thus we anticipate early success; We plan on evaluating our techniques on 10 
+defect datasets that have be gathered in the 
+\href{https://github.com/rahlk/Research/tree/master/Defects/Data}{Promise} 
+repository. Figure \ref{fig2} lists characeteristics of the defect data sets 
+\cite{fayola}.\\[-1cm]
+\end{minipage} \hspace{0.01\linewidth}
+\begin{minipage}{0.5\textwidth}
 	\centering
-\includegraphics[width = 0.7\linewidth]{flowchart}
-\caption{Flowchart of the proposed defect prediction system.}
-\label{fig1}
+	\includegraphics[width = \linewidth]{datasets}
+	\caption{Defect Data Set Characteristics}
+	\label{fig2}
+\end{minipage}
 \end{figure}
-
-\noindent In the planning phase we use training data with recursive 
-\textit{FASTMAP} clustering to create create clusters. For a test data, we 
-generate contrast sets to indicate changes to be made to reduce defects. In the 
-prediction phase, we implement these changes and 
+\begin{thebibliography}{10}
+\bibitem{lessmann}
+Lessmann, S.; Baesens, B.; Mues, C.; Pietsch, S., ``Benchmarking Classification 
+Models for Software Defect Prediction: A Proposed Framework and Novel 
+Findings,'' Software Engineering, IEEE Transactions on , vol.34, no.4, 
+pp.485,496, July-Aug. 2008
+doi: 10.1109/TSE.2008.35
+\bibitem{fayola}
+Peters, F.; Menzies, T., ``Privacy and utility for defect prediction: 
+Experiments with MORPH,'' Software Engineering (ICSE), 2012 34th International 
+Conference on , vol., no., pp.189,199, 2-9 June 2012
+doi: 10.1109/ICSE.2012.6227194
+\end{thebibliography}
 \end{document}

### 2015-01-24 Independent Study '15/Work/compile.sh

@@ -1,0 +1,23 @@
+#!/bin/bash
+if [ -n "$1" ]
+then
+  directory=$1      # If directory name given as a script argument...
+else
+  directory=.   # Otherwise use current working directory.
+fi  
+
+#  Assumes all files in the target directory are tex files,
+#+ with a ".tex" filename suffix.
+
+for file in $directory/*.tex    # Filename globbing.
+do
+	filename=${file%.*x}      #  Strip ".tex" suffix off filename
+                            #+ ('.*x' matches everything
+			    #+ between '.' and 'c', inclusive).
+	echo $filename  
+	
+done
+# Run pdflatex
+/usr/texbin/pdflatex -synctex=1 -interaction=nonstopmode $filename.tex
+# View pdf
+open $filename.pdf
